---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## spaceRATScaffolds

This package contains scaffolds used for
[spaceRAT](https://github.com/shdam/spaceRAT). 
See the package vignettes for instructions how to build and use the scaffolds.

## Installation

Install from GitHub

``` {r, eval = FALSE}
# Install using remotes
# install.packages("remotes")
remotes::install_github("shdam/spaceRATScaffolds", build_vignettes = TRUE)
```


## Usage

This is a data package.
The current `spaceRAT` scaffolds include:

```{r scaffolds}

library("spaceRATScaffolds")

listScaffolds()

listDatasets()

listConverters()
```

### Get scaffold

```{r scaffold}
scaffold <- getScaffold("DMAP")

# Add versioning to get a specific version:
scaffold.v1 <- getScaffold("DMAP.v1", store = TRUE, path = "scaffolds")
```

If you set `store = TRUE`, the scaffold will be stored locally in the folder
set by `path`.
When re-acquiring the scaffold, `getScaffold("DMAP.v1", path = "scaffolds")`
will load the local scaffold instead of downloading from Zenodo.

<!-- 
### Get scaffolds with SciDataFlow 

The scaffolds are managed with 
[SciDataFlow](https://github.com/vsbuffalo/scidataflow). 
If you have it installed, you can download all scaffolds with
`sdf pull` after cloning the repository.  

This will put the scaffolds in `inst/extdata`. 
Therefore, set `path = "inst/extdata"` when loading the scaffold 
with `getScaffold()`. 
-->

### Load test data

```{r loading}

# Load test data 
testData <- loadData("DMAP_exprs")
testPheno <- loadData("DMAP_pData")
```

### Using spaceRAT

See [spaceRAT](https://github.com/shdam/spaceRAT) for instructions on how
to use the scaffolds.

## Report issues

If you have any issues or questions regarding the use of `spaceRATScaffolds`, please do not hesitate to raise an issue on GitHub.
In this way, others may also benefit from the answers and discussions.
